A simplified dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses

### 2016-09-21 Rmd/JTB_ms.Rmd
Numerical analysis and model behavior text

bibliography: ~/library.bib
output: 
  rticles::elsevier_article:
    fig_caption: yes
header-includes:
  - \usepackage{tabularx}
---

>>>>

bibliography: ~/library.bib
output: 
  rticles::elsevier_article:
    fig_caption: yes
---
```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r load, include=FALSE}
# Source default parameters and functions
sapply(list.files(path="../../R", pattern="*.R", full.names=T), source, .GlobalEnv)
```

### 2016-09-21 Rmd/JTB_ms.tex
Numerical analysis and model behavior text

>>>>

To analyze qualitative behavior, we ran the model to steady state across
gradients of external irradiance and DIN, and plotted the specific
growth rate (Fig. 2A) and symbiont to host biomass ratio (Fig. 2B).
Results are consistent with observations in corals: specific growth
rates

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Steady state values of (A) specific growth
(\(Cmol \cdot Cmol^{-1} \cdot d^{-1}\)) and (B) the symbiont to host
biomass ratio (\(CmolS \cdot CmolH^{-1}\)) across gradients of external
irradiance and dissolved inorganic nitrogen. Simulations for each
combination of light and nutrients (21 points along each axis) were run
for 100 days with a time step of 1 day. Negative steady state growth
rates, and corresponding S:H ratios, were set to zero.}
\end{figure}
